% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{xspace}
\usepackage[utf8x]{inputenc}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage{amsmath}

\def\name{Merlin Rabens}
\def\footerlink{https://github.com/bluedigits/cv/blob/master/cv.pdf}

% PDF metadata
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {software development, site reliability, algorithms, computer science},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\newenvironment{no-indent-itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0em}
  }
}{
  \end{list}
}

\def\tilde{$\scriptstyle\sim$}
\def\bullet{$\circ$\xspace}

\begin{document}

{\huge \name}

\bigskip
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{llll}
    Mobile: & On request
      & Github: &\href{http://github.com/bluedigits}{\tt http://github.com/bluedigits}\\
    Email: & \href{mailto:m.rabens@hotmail.de}{\tt m.rabens@hotmail.de} \\
    Languages: & \textsc{en}, \textsc{de}, \textsc{es}
  \end{tabular}
\end{minipage}

\bigskip
\textsc{Keywords}:
SRE, Cloud, Scala ecosystem, Java ecosystem, Containerization, NoSQL, Microservices, Linux.

\section*{Employment}
\begin{no-indent-itemize}
  \item \textsc{Intent HQ}, Barcelona, Site Reliability Engineer, Apr 2021--present.
  \begin{itemize}
    \item\bullet Currently working on a crossplane-powered self-serve platform for developers.
    \item\bullet Devised CI/CD strategies and helped teams automate their release pipelines
    \item\bullet Integrated a cross-site code delivery solution and integrated on-site at the client's premises
    \item\bullet Worked closely with the leadership team to define quarterly SRE goals.
    \item\bullet Devised a strategy to grow and lead a future SRE team.
    \item\bullet Managed the GitHub Enterprise organisation, teams, and workflows as the GitHub admin
    \item\bullet Set up autoscaling strategies to accommodate to the scaling-needs of our backend services.
    \item\bullet Wrote easy-to-follow run-books to help engineers with troubleshooting incidents.
    \item\bullet Helped defining and embracing a "blameless" culture.
    \item\bullet Coached teams on how to define and measure service success and customer happiness.
    \item\bullet Implemented incident response processes end-to-end from alerting to doing post-mortems.
    \item\bullet Implemented and integrated custom SOC2-compliant deployment and release processes.
  \end{itemize}
  \item \textsc{Intent HQ}, Barcelona, Senior Scala Engineer, Oct 2020--Mar 2021.
  \begin{itemize}
    \item\bullet Developed and maintained Intent HQ's data processing platform.
    \item\bullet Conducted interviews to grow Intent HQ's engineering teams.
  \end{itemize}
  \item \textsc{letgo}, Barcelona, Scala Backend Engineer, Jul 2018--Aug 2020.
  \begin{itemize}
    \item\bullet Built user retention by working on campaign and notification backend services.
    \item\bullet Developed and maintained Akka Cluster-powered chat systems for letgo's classified market apps.
    \item\bullet Developed and maintained letgo's searching platform.
  \end{itemize}
  \item \textsc{Syniverse Technologies Messaging GmbH}, Würzburg, Software Engineer, October 2015--Jun 2018.
  \begin{itemize}
    \item\bullet Developed and maintained software for intelligent message processing and routing.
    \item\bullet Built up and maintained a CI environment.
    \item\bullet Extended and maintained a K8s-based production-like test environment.
    \item\bullet Built, managed, and deployed software releases.
    \item\bullet General developer work in Scala and Java, from requirements to delivery.
  \end{itemize}
  \item \textsc{Vogel Druck und Medienservice GmbH}, Höchberg, Senior Software Developer, Nov 2013--Sep 2015.
  \begin{itemize}
    \item\bullet Developed and maintained software for product information management.
    \item\bullet Developed an individual web solution for publication planning of catalogues and brochures.
  \end{itemize}
  \item \textsc{fidelis HR GmbH}, Würzburg, Software Developer, Jul 2011--Oct 2013.
  \begin{itemize}
    \item\bullet Developed and maintained software for payroll accounting.
  \end{itemize}
  \item \textsc{Trinodis GmbH}, Würzburg, Software Developer, Apr 2011--Jun 2011.
  \begin{itemize}
    \item\bullet Developed and maintained web-based software for goods management.
  \end{itemize}
  \item \textsc{DialogData GmbH \& Co. KG}, Munich, Software Developer, Jul 2010--Mar 2011.
  \begin{itemize}
	\item\bullet Implemented requirements for a globally integrated production control system.
	\item\bullet Prototyped and responsible for architecture of an address broker webservice.
	\item\bullet Developed a comprehensive user interface to bring all products under the same roof.
	\item\bullet Integrated key component together with a Spanish engineering team on site.
    \item\bullet Collaborated with UX and product teams to assess requirements.
  \end{itemize}
    \item \textsc{AuDaCon AG}, Weikersheim, Application Developer, Sep 2009--Jun 2010.
  \begin{itemize}
    \item\bullet Developed an efficient online processing platform for transparent cost control of leasing vehicles.
    \item\bullet Integrated electronic approval processes according to individual specifications of leasing companies.
  \end{itemize}
    \item \textsc{Ancud IT-Beratung GmbH}, Nuremberg, Software Developer, Nov 2007--Jun 2009.
  \begin{itemize}
    \item\bullet Implemented requirements for a complete ship monitoring system.
    \item\bullet Developed and designed an uniform land portal and adapted portals for shipowners.
    \item\bullet Developed a portlet for displaying ship routes, current ship positions, and signal strengths.
    \item\bullet Implemented a traffic quota system for ship's crew members.
    \item\bullet Developed a remote control portlet to telecommand ship's PCs.
  \end{itemize}
\end{no-indent-itemize}

\section*{Education}
\begin{no-indent-itemize}
  \item Computer Science Expert Subject Area: Software Development, IHK, 2004--Jul 2007
\end{no-indent-itemize}

\section*{Continuous Learning and Certifications}
\begin{no-indent-itemize}
  \item CPRIME - Certified Site Reliability Engineer
  \item AWS Certified Solutions Architect - Associate
  \item Functional Programming Principles in Scala by EPFL on Coursera
        (\href{https://tinyurl.com/y4fmkg8s}{https://tinyurl.com/y4fmkg8s}), score~100\%
\end{no-indent-itemize}

\bigskip
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
